---
title: "Cait Harrigan, MSc."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```


```{r entries-setup, ehcho=F, warning=F, message=F}
source('format_entries.R')
cv_entries <- cv_entries %>% subset(cv_long_show == T)
```

<div id=cv_print_header>
<center>
<p style="font-size: 15pt; font-weight:300; margin-bottom: 0.5em">
Cait Harrigan, MSc.
</p>

<p style="font-weight:400; margin-bottom: 0.5em">
<i class="fa-solid fa-envelope"></i> charrigan@cs.toronto.edu &nbsp;&nbsp; <i class="fa-solid fa-globe"></i> caitharrigan.ca   &nbsp;&nbsp;  <i class="fa-brands fa-github"></i> harrig12 
</p>
</center> 
</div>


::: {.column-margin}

<a id=print_button href="files/cv.pdf" class="btn btn-outline-primary"><i class="fa-solid fa-download fa-xs"></i> Download as PDF</a>

:::

I am a PhD candidate at the University of Toronto supervised by [Quaid Morris](https://www.morrislab.ca/) and [Kieran Campbell](https://www.camlab.ca/). I am a Doctoral Fellow at the [UofT Data Sciences Institute](https://datasciences.utoronto.ca/) and a graduate researcher at the [Vector Institute](https://vectorinstitute.ai/) and [Ontario Institute for Cancer Research](https://oicr.on.ca/). I use machine learning to understand cancer genomics by modelling the evolutionary constraints that underlie how mutations occur in DNA. I'm passionate about open science, and promoting great mentorship in the sciences.


## Education

`r cv_entries %>% filter(type=='education') %>% print_section()`


## Research experience 

`r cv_entries %>% filter(type=='work') %>% print_section()`

## Fellowships & Awards

`r cv_entries %>% filter(type=='grant' | type=='award') %>% print_section(squish=T)`

## Peer Reviewed Publications

\* Indicates equal contribution


`r cv_entries %>% filter(grepl("publication_reviewed", type)) %>% mutate(when = NA) %>% print_section() %>% gsub(pattern = 'Caitlin F. Harrigan', replacement = '**Caitlin F. Harrigan**')`

## Other Publications

`r cv_entries %>% filter(grepl("publication_other", type)) %>% mutate(when = NA) %>% print_section() %>% gsub(pattern = 'Caitlin F. Harrigan', replacement = '**Caitlin F. Harrigan**')`

## Posters

`r cv_entries %>% filter(type=='poster') %>% print_section(squish=T)`


## Academic Talks 

`r cv_entries %>% filter(type=='talk_academic') %>% print_section(squish=T)`

## Guest Lectures

`r cv_entries %>% filter(type=='guest_lecture') %>% print_section(squish=T)`

## Other Talks

`r cv_entries %>% filter(type=='talk_other') %>% print_section(squish=T)`


## Academic service

```{r, echo=F, warning=F, message=F}
# collate all service together
s1 <- c(
    '<div class= short-entry>',
    "<b>Jouranl peer review:</b> ",
    cv_entries %>% 
      filter(type == 'service_referee_journal') %>% 
      summarize_multi_year(),
    '</div>'
)

s2 <- c(
    '<div class= short-entry>',
    "<b>Conference referee:</b> ", 
    cv_entries %>% 
      filter(type == 'service_referee_conference') %>% 
      summarize_multi_year(),
    '</div>'
)

s3 <- c(
    '<div class= short-entry>',
    "<b>Conference program committee:</b> ", 
    cv_entries %>% 
      filter(type == 'service_pc') %>% 
      summarize_multi_year(),
    '</div>'
)

```

`r HTML(s1)`
`r HTML(s2)`
`r HTML(s3)`

## Student supervision

`r cv_entries %>% filter(type=='supervision') %>% print_section()`

## Progam Administration

`r cv_entries %>% filter(type=='program_admin') %>% print_section()`

## Teaching Assistant Positions

<em style="font-size:0.8em">Unless otherwise noted, school is University of Toronto</em>

`r cv_entries %>% filter(type=='teaching') %>% print_section()`


## Mentorship activities

As part of my ongoing commitment to supporting students at all levels and background in engaging with computational biology, I make an effort to be available to provide guidance and resources to students, with a particular focus on creating an inclusive environment that fosters diverse perspectives and experiences. In addition to being a mentor through the organized programs listed here, I set aside ~2h/month for by-request 30 minute meetings.

`r cv_entries %>% filter(type=='mentorship') %>% print_section()`

## Professional training & Certifications

`r cv_entries %>% filter(type=='professional_development') %>% print_section()`
  
## Hackathons

`r cv_entries %>% filter(type=='hackathon') %>% print_section()`

## Community activities

`r cv_entries %>% filter(type=='volunteering') %>% print_section()`


---

When I'm not doing the above, I like to play ultimate frisbee, scrabble, and I was once a competitive trampolinist at the national level.

<center>
Last updated: `r paste(lubridate::month(Sys.Date(), label=T), lubridate::year(Sys.Date()) )`
</center>