---
title: "Cait Harrigan, MSc, PhD"
format:
  html:
    toc: true
    toc-location: left
---

```{r entries-setup, echo=F, warning=F, message=F}
source('static/format_entries.R')
cv_entries <- cv_entries %>% subset(cv_show == T)
```


::: {id=cv_print_header}

<i class="fa-solid fa-envelope"></i> charrigan@cs.toronto.edu &nbsp;&nbsp; <i class="fa-solid fa-globe"></i> caitharrigan.ca   &nbsp;&nbsp;  <i class="fa-brands fa-github"></i> harrig12 


:::


I am a postdoctoral researcher in the [Park lab](https://compbio.hms.harvard.edu/) at Harvard Medical School. I use machine learning to study cancer evolution and the selective forces shaping tumor development. I earned my PhD in Computer Science from the University of Toronto in 2026, supervised by [Quaid Morris](https://www.morrislab.ca/) and [Kieran Campbell](https://www.camlab.ca/). I was a Doctoral Fellow at the [UofT Data Sciences Institute](https://datasciences.utoronto.ca/) and a graduate researcher at the [Vector Institute](https://vectorinstitute.ai/) and [Ontario Institute for Cancer Research](https://oicr.on.ca/). In my thesis, I developed probabilistic models and Bayesian optimization approaches to study DNA repair deficiencies using genomic sequencing and spatial proteomic data. I'm passionate about open science, and promoting great mentorship in the sciences. 

## Research interests 

My research focuses on developing machine learning methods to understand cancer evolution through patterns in somatic mutations. I combine computational biology, statistical modeling, and large-scale genomic data analysis to identify the evolutionary constraints that underlie mutation, and identify therapeutically targetable DNA repair deficiencies. With expertise in: cancer genomics, spatial proteomics, deep learning, probabilistic modelling, and programming in python & R in HPC environments.


## Education

`r cv_entries %>% filter(type=='education') %>% print_section()`

## Research experience 

`r cv_entries %>% filter(type=='work') %>% print_section()`

## Publications

\* Indicates joint first authorship, † co-corresponding authorship  


`r cv_entries %>% filter(grepl("publication", type)) %>% mutate(bold = paste0(row_number(), ". ", bold), regular1 = gsub(regular1, pattern = 'Caitlin F. Harrigan', replacement = '<u>Caitlin F. Harrigan</u>'), when=NA) %>% print_section(full_width=T, squish=T)`


## Academic talks 

`r cv_entries %>% filter(type=='talk_academic') %>% print_section(squish=T)`

## Academic awards

`r cv_entries %>% filter(type=='award') %>% print_section()`

## Grants

`r cv_entries %>% filter(type=='grant') %>% print_section()`


## Academic service

```{r, echo=F, warning=F, message=F}
# collate all service together
s1 <- c(
    '<div class= short-entry>',
    "<b>Journal peer review:</b> ",
    cv_entries %>% 
      filter(type == 'service_referee_journal') %>% 
      summarize_multi_year(),
    '</div>'
)

s2 <- c(
    '<div class= short-entry>',
    "<b>Conference referee:</b> ", 
    cv_entries %>% 
      filter(type == 'service_referee_conference') %>% 
      summarize_multi_year(),
    '</div>'
)

s3 <- c(
    '<div class= short-entry>',
    "<b>Conference program committee:</b> ", 
    cv_entries %>% 
      filter(type == 'service_pc') %>% 
      summarize_multi_year(),
    '</div>'
)

```

`r HTML(s1)`
`r HTML(s2)`
`r HTML(s3)`


## Professional training 

`r cv_entries %>% filter(type=='professional_development') %>% print_section()`
  


## Student supervision

`r cv_entries %>% filter(type=='supervision') %>% print_section(squish=T)`

## Guest lectures

`r cv_entries %>% filter(type=='guest_lecture') %>% print_section(squish=T)`

## Other talks

`r cv_entries %>% filter(type=='talk_other') %>% print_section(squish=T)`

## Progam & event organization

`r cv_entries %>% filter(type=='program_admin' | type == 'event_org') %>% print_section()`


## Teaching assistant positions

<em style="font-size:0.8em">Unless otherwise noted, school is University of Toronto</em>

`r cv_entries %>% filter(type=='teaching') %>% print_section(squish=T)`


## Mentorship activities

As part of my ongoing commitment to supporting students at all levels and background in engaging with computational biology, I make an effort to be available to provide guidance and resources to students, with a particular focus on creating an inclusive environment that fosters diverse perspectives and experiences. In addition to being a mentor through the organized programs listed here, I set aside ~2h/month for by-request 30 minute meetings.

<br>

`r cv_entries %>% filter(type=='mentorship') %>% print_section(squish=T)`

<br>

## Hackathons

`r cv_entries %>% filter(type=='hackathon') %>% print_section(squish=T)`

## Community activities

`r cv_entries %>% filter(type=='volunteering') %>% print_section(squish=T)`
  
<br>


<center>
Last updated: `r paste(lubridate::month(Sys.Date(), label=T), lubridate::year(Sys.Date()) )`
</center>